3D MAGNETIC MODELLING FOR ELIPSOIDS

### 2016-11-28 manuscript/Paper-magnetic-elipsoid_metodologia.tex
Atualizacao da introducao

The magnetic method is considered one of the oldest geophysics techniques. The greek philosofer Thales supposedly did the first obsevations on magnetism in the sixth century. The chineses in the XII century, already used magnetic compasses as an instrument for marine orientation \citep{nabighian2005historical}. During the World War II there was a need for instruments of several magnitudes of precision higher than was available at the time for the detection of submarines trough aeromagnetic exploration. Thus, the fluxgate magnetometer was invented, expanding the use of this method for geophysic exploration \citep{reford1964aeromagnetics,hanna1924some}. The diffusion of this method was quick and well accepted whereas the possiblity  of covering large areas in a relatively short time \citep{blakely1996potential,nabighian2005historical}.

The applications of magnetic exploration includes several important study situations, as estimating the average of basement relief, mapping geologic structures as faults and lithologic contacts; and also for mineral exploration, identifying mineral deposits and mapping geologic traps for oil and gas  \citep{oliveira2015estimation}.

@@

In his book \textit{A Treatise on Electricity and Magnetism}, \cite{maxwell1881treatise} demonstrated that only shapes bounded by second degree surfaces are uniformly magnetized when placed in a uniform field. In the particular case of the elipsoidal geometry, the intern magnetic field is independent of spatial coordinates, therefore its magnetization is completely homogeneous, making it the only geometric shape that has a true analitic solution for self-desmagnetization \citep{clark1986magnetic}.

The magnetic field resultant of an elipsoid was presented the first time in full modeling in the space domain by \cite{emerson1985magnetic}, along a compilation of several others geometric shapes. Through a consistent notation this work tapped a hole in the literature that missed the elipsoidal model. This model, however, consists in a division between prolate and oblate ellipsoids, with a few differences in the algorithm.

In this work, we will implement a generalized model for triaxial ellipsoids published by \cite{clark1986magnetic}. From the solution of gravitational potential for uniform elipsoids, formally solved by \cite{dirichlet1839nouvelle} in his article \textit{Sur un nouvelle methode pour la determination des integrales multiples}, that uses first and second Legendre's normal elliptic integrals, and using the Poisson's relation \citep{grant1965interpretation} it is possible to calculate the magnetic potential, and posteriorly the magnetic field generated by the body calculating the gradient of this potential.

>>>>

In the 19th century \cite{dirichlet1839nouvelle}, manage to solve the problem of the potential of a homogeneous ellipsoid with semi-axes $a \ge b \ge c$ by using the first and second Legendre's normal elliptic integrals.

In the late 19th century \cite{maxwell1881treatise}, showed that only bodies of second degree can be uniformly magnetized when placed in a uniform field. He also presented the formulae of the demagnetizing field in a uniformly magnetized ellipsoid of revolution.

\cite{osborn1945demagnetizing}, published formulas for the demagnetizing factors of the general ellipsoid alongside with a table of values for different proportions of semi-axis

\cite{stoner1945xcvii}, presented a more simple and friendly formulae of the demagnetizing factors for an ellipsoid, with step-by-step deduction. This work includes formulae for different parametrizations for the ellipsoid (triaxial, prolate, oblate).

\cite{peake1953magnetic} published the formulas for the external field of ellipsoid of revolution in terms of elliptical integrals for external fields.

\cite{chang1961fields} published the formulas for the external field of triaxial, prolate and oblate ellipsoids in terms of elliptical integrals for external fields.

@@

The magnetic field resultant of an ellipsoid was presented the first time in full modeling in the space domain by \cite{emerson1985magnetic}, along a compilation of several others geometric shapes. Through a consistent notation this work tapped a hole in the literature that missed the ellipsoidal model. This model, however, consists in a division between prolate and oblate ellipsoids, with a few differences in the algorithm.
A generalized model for triaxials ellipsoids was published by \cite{clark1986magnetic}. Both in Emerson et al. and Clark et al. works, they were the firsts to include the calculations of the magnetic field in a different coordinate system other than with the position $(0,0,0)$ in the center of the ellipsoid (through a matrix of rotation). However, the codes presented for HP-41C are outdated and doesn't have a detailed descrition of the algorithm.

\cite{tejedor1995external}, presented a work where they calculate the external field generated by ellipsoids using a variational method, in contrast to the usual method of Dirichlet.

\cite{guo1998self}, showed three case studies of the importance of self-demagnetization of high susceptibilties bodies when modelling magnetic sources. A magnetic-iron deposit, volcanic-hosted iron deposit and an ultramafic-hoste nickel andcopper deposits.

\cite{guo2001systematic}, published another paper analysing the errors of what an uncorrected by demagnetization data can affect on anmalies interpretation.
